Frugivore occurrence subset by species with complete trait records

### 2023-11-02 code/L1/L1_F3_TropicalAndes_frug_occ.Rmd
update header info

---
title: "Frugivore occurrence subset by species with complete trait records"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script subsets frugivore occurrence data to species with complete trait coverage."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

>>>>

---
title: "Frugivore occurrence subset by species with complete trait records"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script subsets frugivore occurrence data to species with complete trait coverage."
data input: "TropicalAndes_Frugivoria_traits_subset.csv", "TropicalAndes_GBIF_frugivore_occ_cleaned.csv"
data output: "TropicalAndes_GBIF_frugivore_occ_cleaned_subset.csv"
date: "2023-10-04"
output: html_document
---
